\bf A note on the instability and degeneracy of deep learning models

### 2017-09-30 writing/paper-note/docs/note.tex
backto tech

\documentclass[12pt]{article}
\usepackage{amsmath,amssymb}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL

\usepackage{longtable,booktabs}
\usepackage[unicode=true]{hyperref}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

\newcommand{\Gamc}{C_{N}(\boldsymbol \theta_N) }
\newcommand{\Gamt}{\Gamma_{N,2}(\boldsymbol \theta_N) }

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{-.3in}%
\addtolength{\topmargin}{-.8in}%

@@

\date{}
\maketitle
\begin{abstract}
A probability model exhibits instability if small changes in a data
outcome result in large, and often unanticipated, changes in
probability. For correlated data structures found in several application
areas, there is increasing interest in predicting/identifying such
sensitivity in model probability structure. We consider the problem of
quantifying instability for general probability models defined on
sequences of observations, where each sequence of length \(N\) has a
finite number of possible outcomes. A sequence of probability models
results, indexed by \(N\), that accommodates data of expanding
dimension. Model instability is formally shown to occur when a certain
log-probability ratio under such models grows faster than \(N\). In this
case, a one component change in the data sequence can shift probability
by orders of magnitude. Also, as instability becomes more extreme, the
resulting probability models are shown to tend to degeneracy, placing
all their probability on potentially small portions of the sample space.
These results on instability apply to large classes of models commonly
used in random graphs, network analysis, and machine learning contexts.
\end{abstract}
\noindent%
{\it Keywords:}  Degeneracy, Instability, Classification, Deep Learning, Graphical Models
\vfill

\newpage
\spacingset{1.45}

>>>>

\documentclass[]{article}
%\usepackage{nips15submit_e,times}
\usepackage{url}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{longtable,booktabs}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={A note on the instability and degeneracy of deep learning models},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{5}

% Tech stuff starts here
\usepackage{psfrag,epsf}
%\pdfminorversion=4

@@

\newcommand{\Gamc}{C_{N}(\boldsymbol \theta_N) }
\newcommand{\Gamt}{\Gamma_{N,2}(\boldsymbol \theta_N) }
\bigskip

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%

@@

\maketitle
\begin{abstract}
A probability model exhibits instability if small changes in a data
outcome result in large, and often unanticipated, changes in
probability. For correlated data structures found in several application
areas, there is increasing interest in predicting/identifying such
sensitivity in model probability structure. We consider the problem of
quantifying instability for general probability models defined on
sequences of observations, where each sequence of length \(N\) has a
finite number of possible outcomes. A sequence of probability models
results, indexed by \(N\), that accommodates data of expanding
dimension. Model instability is formally shown to occur when a certain
log-probability ratio under such models grows faster than \(N\). In this
case, a one component change in the data sequence can shift probability
by orders of magnitude. Also, as instability becomes more extreme, the
resulting probability models are shown to tend to degeneracy, placing
all their probability on potentially small portions of the sample space.
These results on instability apply to large classes of models commonly
used in random graphs, network analysis, and machine learning contexts.
\end{abstract}
\noindent%
{\it Keywords:}  Degeneracy, Instability, Classification, Deep Learning, Graphical Models
\vfill

\hfill {\tiny technometrics tex template (do not remove)}
\newpage
\spacingset{1.45} % DON'T change the spacing!
